  \input{header}
  \usepackage{swhap}
  \usepackage{lastpage}
  \shortreporttitle{SWHAP}
  \reportkind{SWHAP Guidelines}
  \reporttitle{Software Heritage Acquisition Process}
  \reportversion{1.1}
  \reportauthorlist{{\bf Authors:} & Laura Bussi, Dept. of Computer Science, University of Pisa $\langle${\tt l.bussi1@studenti.unipi.it}$\rangle$\\&Roberto Di Cosmo, Software Heritage, Inria and University of Paris $\langle${\tt roberto@dicosmo.org}$\rangle$\\&Mathilde Fichen, Software Heritage and CNAM $\langle${\tt mathilde.fichen@inria.fr}$\rangle$\\& Carlo Montangero, Dept. of Computer Science, University of Pisa $\langle${\tt carlo@montangero.eu}$\rangle$\\& Guido Scatena, Dept. of Computer Science, University of Pisa $\langle${\tt guido.scatena@unipi.it}$\rangle$\\}
  \setcounter{secnumdepth}{2}
  \reportabstract{
    The source code of landmark legacy software is particularly important: it sheds
  insights in the history of the evolution of a technology that has changed the
  world, and tells a story of the humans that dedicated their lives to it.\\
  Rescuing it is urgent, collecting and curating it is a complex task that
  requires significant human intervention.\\
This document is a practical, simplified, step-by-step guide to the Software Heritage Acquisition Process (SWHAP). Its aim is to provide tools and guidelines to properly archive source code of historical and scientific relevance in the Software Heritage Universal Archive. This updated guide builds upon the original SWHAP guide, which was initially published in 2019 as a result of a fruitful collaboration between the University of Pisa and Software Heritage in this area of research, under the auspices of UNESCO. It has been validated using a selection of software source code produced in the Pisa area over the past 50 years.

The original guide remains the reference for the global approach adopted and the conceptual choices made. This updated guide aims to offer a simplified, practical implementation of SWHAP.
  \\[2em]
  \paragraph{Acknowledments}
  The authors would like to acknowledge UNESCO for providing the funding that supported the development of this guide.
  \vfill
  \paragraph{License}
  This work is distributed under the terms of the \href{https://creativecommons.org/licenses/by/4.0/}{Creative Commons license CC-BY 4.0}
  }
